{\helveticaitalic{Supplementary Material}}

### 2022-05-03 tex/supplementary.tex
Add gsup value to supplementary materials

\section{Model equations and parameters}
The asymptotic function for the calcium conductance $m_{\infty}$ is given by
\begin{equation}
	m_{\infty}(v) = \frac{1}{2}\left(1+\tanh{\left((v-v_{A})/v_{B}\right)}\right).
\end{equation}
The voltage and potassium nullclines, \(v_{\infty}(v)\) and \(w_{\infty}(v)\), are
\begin{align}
	v_{\infty}(v) & = \frac{-g_{l}(v-v_{l}) - g_{ca}m_{\infty}(v)(v-v_{ca}) + I - \bar g s(v-v_{s})}{g_{k}(v-v_{k})},
	\\
	w_{\infty}(v) & = \frac{1}{2}\left(1+\tanh{\left((v-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
	\caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
	\centering
	\begin{tabular}{ll}
		Parameter                        & value                 \\
		\hline
		                                 &                       \\
		$g_{\leak}$                      & $0.15$ \si{mS/cm^2}   \\
		$g_{\ca}$                        & $0.3$ \si{mS/cm^2}    \\
		$g_{\k}$                         & $0.6$ \si{mS/cm^2}    \\
		$v_{\leak}$                      & $-50$ \si{mV}         \\
		$v_{\ca}$                        & $100$ \si{mV}         \\
		$v_{\k}$                         & $-70$ \si{mV}         \\
		$v_{A}$                          & $1$ \si{mV}           \\
		$v_{B}$                          & $14.5$ \si{mV}        \\
		$v_{C}$                          & $4$ \si{mV}           \\
		$v_{D}$                          & $15$ \si{mV}          \\
		$I$                              & $3.8$ \si{\mu A/cm^2} \\
		$\tau_w$                         & $100$ \si{ms}         \\
		$\tau_a$                         & $1000$ \si{ms}        \\
		$\tau_b$                         & $100$ \si{ms}         \\
		$\tau_\kappa$                    & $100$ \si{ms}         \\
		$v_{\theta}$                     & $0$ \si{mV}           \\
		$v_{s}$                          & $-80$ \si{mV}         \\
		$T$                              & $376$ \si{ms}         \\
		$T_{a}$                        & $49$ \si{ms}          \\
		$T_{s}$                      & $327$ \si{ms}         \\
		$g^{\star}$                      & $0.0068$ \si{mS/cm^2} \\
		$g_{bif}$                        & $0.0038$ \si{mS/cm^2} \\
		$\lambda:=\exp(-T_{a}/\tau_b)$ & $0.612$               \\
		$\rho:=\exp(-T_{s}/\tau_a)$  & $0.721$               \\
	\end{tabular}
\end{table}

>>>>

\section{Model equations and parameters}
The asymptotic function for the calcium conductance $m_{\infty}$ is given by
\begin{equation}
	m_{\infty}(v) = \frac{1}{2}\left(1+\tanh{\left((v-v_{A})/v_{B}\right)}\right).
\end{equation}
The voltage and potassium nullclines, \(v_{\infty}(v)\) and \(w_{\infty}(v)\), are
\begin{align}
	v_{\infty}(v) & = \frac{-g_{l}(v-v_{l}) - g_{ca}m_{\infty}(v)(v-v_{ca}) + I - \bar g s(v-v_{s})}{g_{k}(v-v_{k})},
	\\
	w_{\infty}(v) & = \frac{1}{2}\left(1+\tanh{\left((v-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
	\caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
	\centering
	\begin{tabular}{ll}
		Parameter                      & value                 \\
		\hline
		                               &                       \\
		$g_{\leak}$                    & $0.15$ \si{mS/cm^2}   \\
		$g_{\ca}$                      & $0.3$ \si{mS/cm^2}    \\
		$g_{\k}$                       & $0.6$ \si{mS/cm^2}    \\
		$v_{\leak}$                    & $-50$ \si{mV}         \\
		$v_{\ca}$                      & $100$ \si{mV}         \\
		$v_{\k}$                       & $-70$ \si{mV}         \\
		$v_{A}$                        & $1$ \si{mV}           \\
		$v_{B}$                        & $14.5$ \si{mV}        \\
		$v_{C}$                        & $4$ \si{mV}           \\
		$v_{D}$                        & $15$ \si{mV}          \\
		$I$                            & $3.8$ \si{\mu A/cm^2} \\
		$\tau_w$                       & $100$ \si{ms}         \\
		$\tau_a$                       & $1000$ \si{ms}        \\
		$\tau_b$                       & $100$ \si{ms}         \\
		$\tau_\kappa$                  & $100$ \si{ms}         \\
		$v_{\theta}$                   & $0$ \si{mV}           \\
		$v_{s}$                        & $-80$ \si{mV}         \\
		$T$                            & $376$ \si{ms}         \\
		$T_{a}$                        & $49$ \si{ms}          \\
		$T_{s}$                        & $327$ \si{ms}         \\
		$g^{\star}$                    & $0.0068$ \si{mS/cm^2} \\
		$g_{bif}$                      & $0.0038$ \si{mS/cm^2} \\
		$\bar g_{s}$                   & $0.584$ \si{mS/cm^2}  \\
		$\lambda:=\exp(-T_{a}/\tau_b)$ & $0.612$               \\
		$\rho:=\exp(-T_{s}/\tau_a)$    & $0.721$               \\
	\end{tabular}
\end{table}
